\Large \bf Polyglots : Crossing Origins by Crossing Formats

### 2013-02-21 main.tex
Extended evaluation of Alexa top 100

\subsubsection{Syntax injection}
\label{sec:injection}
In a cross-site scripting attack user input is used to compose an HTML document. 
Fragments of HTML-syntax in the input alters the semantic of the document to 
execute attacker supplied 
script code. Similarly, in a syntax injection attack the vulnerable target will 
compose content from attacker controlled input containing syntax of a foreign 
format, thereby creating a polyglot. The polyglot is benign when viewed as the 
original format, but malicious when viewed as the injected format. While the 
targeted service serves the content as its original format, it is in the hands 
of the attacker to decide how it is interpreted.
%
The targeted service is assumed to employ server-side cross-site scripting 
sanitization. Hence, for the attack to be successful, the input must 
bypass this sanitization. The sanitization filter will remove or encode 
problematic characters related to HTML-syntax, based on the context of the web application. In a polyglot attack
the injected format will pose as a new context, unknown to the filter. Chances are that the 
key elements of the injected format will pass the filter unaltered.

@@

\subsubsection{Content smuggling}
\label{sec:smuggling}
The vulnerable target of a content smuggling attack, lets 
users submit files to the service which are subsequently served under the origin of 
the service. Examples of such potentially vulnerable services are file sharing services, image databases, 
social networks, conference management systems or job broker services. Such a service 
accepts a limited set of file-formats, and the files are run through a filter to verify that they 
belong to this set, e.g. images, before being served to the end
user. The
service will verify the file under the assumption that it conforms strictly to one format. 
By submitting a polyglot to such a service, an attacker can evade the filter as the polyglot does conform to the benign format.
Since the attacker can coerce the content to be interpreted as the malicious format, the
service is tricked into serving malicious content.

@@

\begin{table}[h!]
\begin{tabular}{l||c|c|c}
& object & embed & Adobe is default \\ \hline
Firefox & X & X & X \\ \hline
Chrome & X & X & --- \\ \hline
Safari & X & X & X \\ \hline
Opera & X & X & X \\ \hline
Internet Explorer & --- & X & X %\\ \hline
\end{tabular}
\caption{Comparison of browsers}
\label{tab:comparison}
\end{table}
%\subsection{Bypassing content filters}

@@

\subsection{Alexa top 100}
We have conducted a
study to evaluate the prevalence of the problem on popular sites, 
covering the Alexa top 100 websites. Because of their dominance 
on the web, these websites are also the most exposed to security threats.
The study covers PDF-based polyglot attacks using syntax injection as the infiltration method.
It does not involve polyglot attacks based on content smuggling, as 
potential targets generally require authentication before submitting content.
We refrain from mentioning names of individual websites to prevent exploitation 
before the issues have been properly dealt with. Neither do we want to disclose 
these websites as particularly vulnerable.

The study is based on supplying the websites with the benign minimal PDF in 
Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
The sample contains the essential keywords and tokens required to perform a syntax 
injection based polyglot attack. If these tokens pass through unaltered, the website is 
considered vulnerable. Only public accessible input parameters, those that do not require authentication, 
were tested, which suggests that more websites are likely vulnerable in input that do
requires authentication.

The conclusion is 
that nine websites out of the hundred apply insufficient content filtering with 
respect to the PDF format. Out of the nine found to be vulnerable;three were susceptible to traditional 
XSS and thereby also to PDF polyglot attacks, two were susceptible only to PDF based polyglot attacks, and four applied 
insufficient content filtering, but the input was reflected in a way that prevented exploitation, e.g. the header appeared after 1024 bytes.
%
%, which have the potential of compromising the 
%confidentiality and integrity of the website's users.
%
We are in contact with the teams responsible for the websites to help
mitigate the vulnerabilities.

@@

\subsubsection{Content smuggling}

The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
on hosting user-supplied content, is to serve the content from a sandboxed origin that is 
completely separate, as per SOP, and isolated from the sensitive services. 
These best-practices successfully prevents content smuggling 
attacks, as the restrictions of the SOP prevents the content from accessing any sensitive 
resources in the origin of the web service.

>>>>

\subsubsection{Syntax injection}
\label{sec:injection}
In a cross-site scripting attack user input is used to compose an HTML document. 
Fragments of HTML-syntax in the input alters the semantic of the document to 
execute attacker supplied 
script code. Similarly, in a syntax injection attack the vulnerable target will 
compose content from attacker controlled input containing syntax of a foreign 
format, thereby creating a polyglot. The polyglot is benign when viewed as the 
original format, but malicious when viewed as the injected format. While the 
targeted service serves the content as its original format, it is in the hands 
of the attacker to decide how it is interpreted. Examples of 
such services include dynamic user driven websites, e.g. social networks, search engines, etc.
%
The targeted service is assumed to employ server-side cross-site scripting 
sanitization. Hence, for the attack to be successful, the input must 
bypass this sanitization. The sanitization filter will remove or encode 
problematic characters related to HTML-syntax, based on the context of the web application. In a polyglot attack
the injected format will pose as a new context, unknown to the filter. Chances are that the 
key elements of the injected format will pass the filter unaltered.

@@

\subsubsection{Content smuggling}
\label{sec:smuggling}
The vulnerable target of a content smuggling attack, lets 
users submit files to the service which are subsequently served under the origin of 
the service. Examples of such potentially vulnerable services are cloud storage services, image databases, 
social networks, conference management systems or job broker services. Such a service 
accepts a limited set of file-formats, and the files are run through a filter to verify that they 
belong to this set, e.g. images, before being served to the end
user. The
service will verify the file under the assumption that it conforms strictly to one format. 
By submitting a polyglot to such a service, an attacker can evade the filter as the polyglot does conform to the benign format.
Since the attacker can coerce the content to be interpreted as the malicious format, the
service is tricked into serving malicious content.

@@

\begin{table}[h!]
\begin{tabular}{l|c|c|c}
& object & embed & Adobe is default \\ \hline
Firefox & Yes & Yes & Yes \\ \hline
Chrome & Yes & Yes & No \\ \hline
Safari & Yes & Yes & Yes \\ \hline
Opera & Yes & Yes & Yes \\ \hline
Internet Explorer & No & Yes & Yes %\\ \hline
\end{tabular}
\caption{Comparison of browsers}
\label{tab:comparison}
\end{table}
%\subsection{Bypassing content filters}

@@

\subsection{Alexa top 100}
We have conducted two
studies to evaluate the prevalence of the problem on popular sites, 
covering the Alexa top 100 websites. Because of their dominance 
on the web, these websites are also the most exposed to security threats.
The first study covers PDF-based polyglot attacks using syntax injection as the 
infiltration method; the second covers content smuggling.
%It does not involve polyglot attacks based on content smuggling, as 
%potential targets generally require authentication before submitting content.
We refrain from mentioning names of individual websites to prevent exploitation 
before the issues have been properly dealt with. Neither do we want to disclose 
these websites as particularly vulnerable. We are in contact with the teams responsible for the websites to help
mitigate the vulnerabilities.

\paragraph{Syntax injection}
The study is based on supplying the websites with the benign minimal PDF in 
Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
The sample contains the essential keywords and tokens required to perform a syntax 
injection based polyglot attack. If these tokens pass through unaltered, the website is 
considered vulnerable. Only public accessible input parameters, those that do not require authentication, 
were tested, which suggests that more websites are likely vulnerable in input that do
requires authentication.

The conclusion is 
that nine websites out of the hundred apply insufficient content filtering with 
respect to the PDF format. Out of the nine found to be vulnerable; three were susceptible to traditional 
XSS and thereby also to PDF polyglot attacks, two were susceptible only to PDF based polyglot attacks, and four applied 
insufficient content filtering, but the input was reflected in a way that prevented exploitation, e.g. the header appeared after 1024 bytes.
%
%, which have the potential of compromising the 
%confidentiality and integrity of the website's users.
%

The two web sites found susceptible only to polyglot attacks and not XSS attacks
are of particular interest. They both employ proper measures to protect properly 
against XSS attacks, and yet fall short in defeating this new breed of attacks.

\begin{enumerate}
\item The first web site reflected user input in an inline  
JavaScript context, inside a string. To prevent cross-site scripting in this 
context, the following measures were taken: the JavaScript string delimiters 
were properly encoded, the backslash character was properly escaped, and the 
string "$<$/script$>$" was removed. None of these measures prevent an attacker 
from injecting valid PDF syntax.
\item The second website reflected the user input in an HTML-comment context. 
The only measure taken to prevent XSS attacks in this context was removing any 
occurrence of the character sequence "--$>$". Again, while successfully preventing 
XSS attacks, this measure is ineffective in preventing an attacker from injecting PDF syntax.
\end{enumerate}

\paragraph{Content smuggling}
Further, a smaller study was conducted, not covering the full Alexa top 100, but 
targeting popular cloud storage services. 
This study is based on polyglot content being uploaded to the service and 
subsequently analyzed to determine which origin it was served under. One major 
enterprise cloud storage service was found to be susceptible to attacks. The service makes an effort to
follow current best practices, see Section~\ref{sec:smuggling-mitigation}, for almost all uploaded content; the exception being the user's 
avatar images that are served under the sensitive origin. An attacker could 
upload a specially crafted avatar image that, when embedded as PDF on the attackers 
web site, can access and modify the contents of the victim's cloud storage.
We are currently advising the service provider to help mitigate this vulnerability.

@@

\subsubsection{Content smuggling}
\label{sec:smuggling-mitigation}
The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
on hosting user-supplied content, is to serve the content from a sandboxed origin that is 
completely separate, as per SOP, and isolated from the sensitive services. 
These best-practices successfully prevents content smuggling 
attacks, as the restrictions of the SOP prevents the content from accessing any sensitive 
resources in the origin of the web service.
